---
title: "Preparation mouse dataset for PTM project"
output: html_notebook
---
```{r, include=FALSE} 
library(dplyr)
library(ggplot2)
library(rlist)
library(tidyr)
library(ggpubr)
library(stringr)
library(seqinr)
library(IRanges)
library(GenomicRanges)
library(data.table)
```

The mouse (Mus musculus) proteome was obtained from UniProtKB/Swiss-Prot database (reference proteome UP000000589; release 2022_02). Aggregation prone regions (APRs) were predicted computationally using TANGO at physiological conditions (pH at 7.5, temperature at 298 K, protein concentration at 1 mM and ionic strength at 0.15 M). 

```{r, include=FALSE}
tango_APRs <- read.delim("Data/Mouse/TANGO_output/PSX_tangoresidue.out", header=TRUE)
colnames(tango_APRs) <- c("Protein","Position","Residue","tango_Score","length")
tango_APRs$length <- NULL
list_names <- strsplit(as.character(tango_APRs$Protein), "\\|")
res <- matrix(nrow = length(tango_APRs$Protein), ncol = 1)
for (i in 1:length(tango_APRs$Protein)){
  res[i,] <- list_names[[i]][2]
}
tango_APRs$Protein <- res
```

The dataset contains 5783 proteins, after excluding sequences with nonstandard amino acids (e.g. selenocysteine), sequences with <25 amino acids and those with >10,000 residues and after filtering at 90% sequence identity using the CD-hit algorithm.

```{r, include=FALSE}
#cd-hit using the web server with default options
names90 <- read.delim("Data/Mouse/UniProt/mouse_90.fasta", header=FALSE)
list_names <- strsplit(as.character(names90$V1), "\\|")
res <- matrix(nrow = length(names90$V1), ncol = 1)
for (i in 1:length(names90$V1)){
  res[i,] <- list_names[[i]][2]
}
names90$V1 <- res
names90 <- unique(names90)
tango_APRs <- subset(tango_APRs, Protein %in% names90$V1) 
#Remove proteins with less than 25 aa and more that 10,000 aa and define APRs score >10
tango_APRs$length <- 1
proteinsum <- aggregate(length ~ Protein, data=tango_APRs, FUN="sum") 
colnames(proteinsum) <- c("Protein","protein_length")
tango_APRs <- merge(tango_APRs,proteinsum, by="Protein")
length(which(proteinsum$protein_length < 25))
shorties <- tango_APRs[tango_APRs$Protein %in% proteinsum$Protein[proteinsum$protein_length<25],]
master_df <- tango_APRs[!(tango_APRs$Protein %in% shorties$Protein),]
```

Signal peptides and transmembrane domains were identified using deepTMHMM. These were later removed from the analyses to avoid biases.

```{r, include=FALSE}
#First save mouse proteome file
mouse_proteome <- aggregate (Residue ~ Protein, data=master_df, FUN="paste",collapse = "")
colnames(mouse_proteome) <- c("Protein","Sequence")
save(mouse_proteome, file = "Data/RData/Mouse/mouse_proteome.RData")
#Create files for SignalP and TMHMM
write.fasta(as.list(mouse_proteome$Sequence[1:5000]), mouse_proteome$Protein[1:5000], "Data/Mouse/UniProt/1-5000.fa", open = "w", nbchar = 60, as.string = FALSE)
write.fasta(as.list(mouse_proteome$Sequence[5001:10000]), mouse_proteome$Protein[5001:10000], "Data/Mouse/UniProt/5001-10000.fa", open = "w", nbchar = 60, as.string = FALSE)
write.fasta(as.list(mouse_proteome$Sequence[10001:nrow(mouse_proteome)]), mouse_proteome$Protein[10001:nrow(mouse_proteome)], "Data/Mouse/UniProt/10001-end.fa", open = "w", nbchar = 60, as.string = FALSE)
#Transmembrane domains , topology and signal peptides from deepTMHMM (deepTMHMM using biolib webserver)
trans1.5000 <- read.table("Data/Mouse/TMHMM/TMRs_1-5000.gff3", sep=";", quote="\"")
trans5001.10000 <- read.table("Data/Mouse/TMHMM/TMRs_5001-10000.gff3", sep=";", quote="\"")
transend <- read.table("Data/Mouse/TMHMM/TMRs_10001-end.gff3", sep=";", quote="\"")
TMHMM <- rbind(trans1.5000,trans5001.10000,transend)
TMHMM <- subset(TMHMM, V1 != "//")
TMHMM <- cbind(TMHMM, read.table(text = TMHMM$V1, header = FALSE, sep = "\t"))
TMHMM <- subset(TMHMM, select = c(2:5))
colnames(TMHMM) <- c("Protein","Topology","Start","End")
TMHMM <- subset(TMHMM, Protein %in% mouse_proteome$Protein)
dt1 <- as.data.table(TMHMM)
dt2 <- as.data.table(master_df)
gr1 = GRanges(Rle(dt1$Protein), IRanges(as.numeric(dt1$Start), as.numeric(dt1$End)))
gr2 = GRanges(Rle(dt2$Protein), IRanges(as.numeric(dt2$Position),as.numeric(dt2$Position)))
zone.ind <- findOverlaps(gr2, gr1, select="arbitrary")
dt2$Topology <- dt1$Topology[zone.ind]
master_df <- as.data.frame(dt2)
rm(dt2,dt1)
gc()
save(master_df, file = "Data/RData/Mouse/all_tango_res_filtered.RData")
```

In this study, APRs are defined as continuous segments between 5 and 15 amino acids in length, each with an aggregation score of at least 10. Gatekeeper positions (GKPs) are defined as the next three residues immediately downstream and upstream of APRs. All other residues are defined as distal regions.

```{r, include=FALSE}
#Annotate TANGO categories and add avgTANGO per APR and maxTANGO protein
load("Data/RData/Mouse/all_tango_res_filtered.RData")
master_df$APRdef_tango <- "No"
master_df$APRdef_tango[which(master_df$tango_Score > 10)] <- "APR" 
annotateDF <- function(prepare_annotation, a,b,c,d) {
  prepare_annotation$APRdef2_tango <- gsub(a, b, prepare_annotation$APRdef2_tango)
  prepare_annotation$APRdef2_tango <- gsub(c, d, prepare_annotation$APRdef2_tango)
  return(prepare_annotation)
}
master_df3 <- master_df
master_df3$APRdef2_tango <-as.numeric(as.factor(master_df3$APRdef_tango))
master_df3$APRdef2_tango[which(master_df3$APRdef2_tango == 2)] <- 0
prepare_annotation <- aggregate (APRdef2_tango ~ Protein, data=master_df3, FUN="paste",collapse = "")
prepare_annotation2 <- annotateDF(prepare_annotation,"01","21","10","12") #GK_1
prepare_annotation2 <- annotateDF(prepare_annotation2,"02","32","20","23") #GK_2
prepare_annotation2 <- annotateDF(prepare_annotation2,"03","43","30","34") #GK_3
prepare_annotation2 <- paste(prepare_annotation2$APRdef2_tango, collapse="")
prepare_annotation2 <- unlist(strsplit(prepare_annotation2,""))
master_df3$APRdef2_tango <- prepare_annotation2
master_df3$APRdef_tango[which(master_df3$APRdef2_tango == "0")] <- "Distal region"
master_df3$APRdef_tango[which(master_df3$APRdef2_tango == "2")] <- "GK_1"
master_df3$APRdef_tango[which(master_df3$APRdef2_tango == "3")] <- "GK_2"
master_df3$APRdef_tango[which(master_df3$APRdef2_tango == "4")] <- "GK_3"
master_df3$Protein <- as.factor(master_df3$Protein)
prepare_annotation3 <- annotateDF(prepare_annotation,"01","A1","10","1D") #GK_1
prepare_annotation3 <- annotateDF(prepare_annotation3,"0A","BA","D0","DE") #GK_2
prepare_annotation3 <- annotateDF(prepare_annotation3,"0B","CB","E0","EF") #GK_3
prepare_annotation3 <- paste(prepare_annotation3$APRdef2_tango, collapse="")
prepare_annotation3 <- unlist(strsplit(prepare_annotation3,""))
master_df3$Side <- prepare_annotation3
master_df3$Side[which(master_df3$Side %in% c("0","1"))] <- "None"
master_df3$Side[which(master_df3$Side %in% c("A","B","C"))] <- "N_ter"
master_df3$Side[which(master_df3$Side %in% c("D","E","F"))] <- "C_ter"
#Define TANGO APRs ids
tango_APRs <- subset(master_df3, APRdef_tango != "Distal region")
j <- 1
tango_APRs$APRcount_tango <- 0
tango_APRs$APRcount_tango[1] <- 1
for (i in 2:length(tango_APRs$Protein)){
  if (tango_APRs$Protein[i] != tango_APRs$Protein[i-1] | tango_APRs$Position[i] != (tango_APRs$Position[i-1]+1)){
    j <- j + 1
    tango_APRs$APRcount_tango[i] <- j 
  }
  else if (tango_APRs$Side[i-1] == "C_ter" & tango_APRs$APRdef2_tango[i-1] == 4) {
    j <- j + 1
    tango_APRs$APRcount_tango[i] <- j 
  }
  else if (tango_APRs$Side[i-1] == "C_ter" & tango_APRs$APRdef2_tango[i-1] != 4 & tango_APRs$Side[i] != "C_ter") {
    j <- j + 1
    tango_APRs$APRcount_tango[i] <- j 
  }
  else{
    tango_APRs$APRcount_tango[i] <- j 
  }
}
tango_APRs2 <- subset(tango_APRs, select = c(1,2,11))
master_df3 <- merge(master_df3,tango_APRs2, by=c("Protein","Position"),all = TRUE)
master_df3$APRcount_tango[which(is.na(master_df3$APRcount_tango))] <- 0
master_df3$APRdef_tango[which(master_df3$APRcount_tango == 0)] <- "No"
save(master_df3, file = "Data/RData/Mouse/all_tango_res_annotated.RData")
#Summarize TANGO information
load("Data/RData/Mouse/all_tango_res_annotated.RData")
onlyapr_tango <- subset(master_df3, master_df3$APRdef_tango=="APR")
tango_APRs <- aggregate (Residue ~ APRcount_tango, data=onlyapr_tango, FUN="paste",collapse = "")
colnames(tango_APRs) <- c("APRcount_tango","APR")
TotalTANGO <- aggregate (tango_Score ~ APRcount_tango, data=onlyapr_tango, FUN="sum")
colnames(TotalTANGO) <- c("APRcount_tango","TotalTANGO")
lengthAPR <- aggregate (length ~ APRcount_tango, data=onlyapr_tango, FUN="sum")
colnames(lengthAPR) <- c("APRcount_tango","lengthAPR")
startAPR <- aggregate (Position ~ APRcount_tango, data=onlyapr_tango, FUN="min")
colnames(startAPR) <- c("APRcount_tango","startAPR")
endAPR <- aggregate (Position ~ APRcount_tango, data=onlyapr_tango, FUN="max")
colnames(endAPR) <- c("APRcount_tango","endAPR")
proteins_apr <- unique(subset(onlyapr_tango, select = c(1,11)))
topology_apr <- aggregate (Topology ~ APRcount_tango, data=onlyapr_tango, FUN="unique")
tango_APRs <- Reduce(function(x, y) merge(x, y, all=TRUE), list(proteins_apr,tango_APRs,TotalTANGO,lengthAPR,startAPR,endAPR,topology_apr))
tango_APRs$avgTANGO <- tango_APRs$TotalTANGO / tango_APRs$lengthAPR
tango_APRs2 <- subset(tango_APRs, lengthAPR > 4 & lengthAPR < 16 & Topology %in% c("outside","inside")) #From 32478 to 24593
onlyapr_tango <- onlyapr_tango[which(onlyapr_tango$APRcount_tango %in% tango_APRs2$APRcount_tango),]
len_APR <- aggregate (length ~ APRcount_tango, data=onlyapr_tango, FUN="sum")
colnames(len_APR)[2] <- "APR_length"
onlyapr_tango$length <- NULL
onlyapr_tango <- merge(onlyapr_tango,len_APR)
master_df3$APRcount_tango[which(!master_df3$APRcount_tango %in% onlyapr_tango$APRcount_tango)] <- 0
master_df3$APRdef_tango[which(master_df3$APRcount_tango == 0)] <- "Distal region"
master_df3$APRdef2_tango[which(master_df3$APRcount_tango == 0)] <- 0
master_df3$Side[which(master_df3$APRcount_tango == 0)] <- "None"
total_scoreAPR <- aggregate (tango_Score ~ APRcount_tango, data=onlyapr_tango, sum)
colnames(total_scoreAPR) <- c("APRcount_tango","TotalScore")
onlyapr_tango <- merge(onlyapr_tango,total_scoreAPR,by="APRcount_tango")
onlyapr_tango$avgScore <- onlyapr_tango$TotalScore / onlyapr_tango$APR_length
maxAPR_Protein <- aggregate (avgScore ~ Protein, data=onlyapr_tango, max)
colnames(maxAPR_Protein) <- c("Protein","maxProtscore")
onlyapr_tango <- merge(onlyapr_tango,maxAPR_Protein,by="Protein")
temp <- unique(subset(onlyapr_tango, select = c(1,2,11,13)))
temp2 <- unique(subset(onlyapr_tango, select = c(1,14)))
master_df3 <- merge(master_df3,temp,by = c("Protein","APRcount_tango"), all.x = TRUE)
master_df3 <- merge(master_df3,temp2,by = c("Protein"), all.x = TRUE)
master_df3 <- master_df3[order(master_df3$Protein, master_df3$Position),]
rownames(master_df3) <- NULL
master_df3$maxProtscore[which(is.na(master_df3$maxProtscore))] <- 0
master_df3$avgScore[which(is.na(master_df3$avgScore))] <- 0
master_df3$APR_length[which(is.na(master_df3$APR_length))] <- 0
save(master_df3, file = "Data/RData/Mouse/master_df.RData")
save(tango_APRs, file = "Data/RData/Mouse/tango_APRs_ALL.RData")
save(tango_APRs2, file = "Data/RData/Mouse/tango_APRs.RData")
```

Since TANGO calculations of the aggregation propensity incorporate the effects of GKs, we also included a second step in the calculation, in which we recalculate the TANGO score of the isolated APRs flanked by Alanines. We called the resulting aggregation propensity score of APRs without the mitigating effect of the flanking GKs the “PureTANGO” score.

```{r, include=FALSE}
load("Data/RData/Mouse/master_df.RData")
pure_tango <- subset(master_df3, master_df3$APRdef_tango=="APR")
pure_tango <- aggregate (Residue ~ APRcount_tango, data=pure_tango, FUN="paste",collapse = "")
pure_tango$Residue <- paste0("A",pure_tango$Residue)
pure_tango$Residue <- paste0(pure_tango$Residue,"A")
write.fasta(as.list(pure_tango$Residue), pure_tango$APRcount_tango, "Data/Mouse/TANGO_output/Pure_tango/pure_tango.fa", open = "w", nbchar = 60, as.string = FALSE)
pure_tango <- read.delim("Data/Mouse/TANGO_output/Pure_tango/PSX_globaltotal.out", header=FALSE)
pure_tango <- subset(pure_tango, select = c(1,3))
colnames(pure_tango) <- c("APRcount_tango","pure_Tango")
master_df3 <- merge(master_df3,pure_tango,all.x = TRUE)
master_df3$pure_Tango <- master_df3$pure_Tango / master_df3$APR_length
master_df3$pure_Tango[which(is.na(master_df3$pure_Tango))] <- 0
master_df3 <- master_df3[order(master_df3$Protein, master_df3$Position),]
rownames(master_df3) <- NULL
save(master_df3, file = "Data/RData/Mouse/master_df.RData")
```

Information on protein subcellular location was extracted from UniProt.

```{r, include=FALSE}
uniprot.proteome <- read.delim("Data/Mouse/UniProt/mouse_proteome_info.tsv")
uniprot.proteome <- subset(uniprot.proteome, select = c(1,8))
colnames(uniprot.proteome) <- c("Protein","Sub_loc")
master_df3 <- merge(master_df3,uniprot.proteome, all.x = TRUE)
master_df3$Nucleus <- "No"
master_df3$Nucleus[which(grepl("ucleus", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
master_df3$Cytoplasm <- "No"
master_df3$Cytoplasm[which(grepl("ytoplasm", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
master_df3$Secreted <- "No"
master_df3$Secreted[which(grepl("ecreted", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
master_df3$Membrane <- "No"
master_df3$Membrane[which(grepl("ell membrane", master_df3$Sub_loc, fixed = TRUE) | grepl("ell projection", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
master_df3$Mitochondrion <- "No"
master_df3$Mitochondrion[which(grepl("itochondrion", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
master_df3$Endoplasmic_reticulum <- "No"
master_df3$Endoplasmic_reticulum[which(grepl("eticulum", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
master_df3$Golgi <- "No"
master_df3$Golgi[which(grepl("olgi", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
master_df3$Lysosome <- "No"
master_df3$Lysosome[which(grepl("ysosome", master_df3$Sub_loc, fixed = TRUE))] <- "Yes"
save(master_df3, file = "Data/RData/Mouse/master_df.RData")
```

ANALYSIS

```{r, include=FALSE}
load("Data/RData/Mouse/master_df.RData")
load("Data/dbPTM/all_PTM_data.RData")
master_df3_filtered <- subset(master_df3, Topology %in% c("inside","outside"))
#PTM ASN predictor based on sequon
all_res <- paste(master_df3_filtered$Residue, collapse = '')
all_res <- gsub('N[^P][ST]', '210', all_res)
all_res <- unlist(strsplit(all_res,""))
master_df3_filtered$glyc <- all_res 
master_df3_filtered$loc <- "No"
master_df3_filtered$loc[which((master_df3_filtered$Nucleus == "No" & master_df3_filtered$Cytoplasm == "No" & master_df3_filtered$Mitochondrion == "No") &
                          (master_df3_filtered$Secreted == "Yes" | master_df3_filtered$Membrane == "Yes" | master_df3_filtered$Endoplasmic_reticulum == "Yes" | master_df3_filtered$Golgi == "Yes" | master_df3_filtered$Lysosome == "Yes") & master_df3_filtered$Topology == "outside")] <- "Extra"
master_df3_filtered$loc[which((master_df3_filtered$Nucleus == "Yes" | master_df3_filtered$Cytoplasm == "Yes" | master_df3_filtered$Mitochondrion == "Yes") &
                          (master_df3_filtered$Secreted == "No" & master_df3_filtered$Membrane == "No" & master_df3_filtered$Endoplasmic_reticulum == "No" & master_df3_filtered$Golgi == "No" & master_df3_filtered$Lysosome == "No") & master_df3_filtered$Topology == "inside")] <- "Intra"
nlinked <- subset(PTMs_df, Type2 == "N-linked Glycosylation_N" & names == "MOUSE", select = c(1,2,4,6))
colnames(nlinked)[3] <- "Residue"
master_df3_filtered$loc[which(master_df3_filtered$Protein %in% nlinked$Protein)] <- "Extra"
master_df3_filtered <- merge(master_df3_filtered, nlinked, by=c("Protein","Position","Residue"), all.x = TRUE)
master_df3_filtered$glyc[which(master_df3_filtered$glyc == 0)] <- as.character(master_df3_filtered$Residue[which(master_df3_filtered$glyc == 0)])
master_df3_filtered$glyc[which(master_df3_filtered$glyc == 1)] <- as.character(master_df3_filtered$Residue[which(master_df3_filtered$glyc == 1)])
master_df3_filtered$glyc[which(master_df3_filtered$glyc == 2)] <- "Sequon"
master_df3_filtered$glyc[which(master_df3_filtered$Type2 == "N-linked Glycosylation_N")] <- "N-linked Glycosylation_N"

types <- c("Sequon.Intra","Sequon.Extra")
bio_mouse = matrix(numeric(length(types)*9), nrow = length(types), ncol = 8)
colnames(bio_mouse) <- c("Distal region","FR3 N-ter","FR2 N-ter","FR1 N-ter","APR","FR1 C-ter","FR2 C-ter","FR3 C-ter")
rownames(bio_mouse) <- types
for (i in 1:length(types)){
  print(i)
  temp_loc <- strsplit(types[i], "\\.")[[1]][2]
  temp_res <- strsplit(types[i], "\\.")[[1]][1]
  asp <- subset(master_df3_filtered, Residue == "N" & loc == temp_loc)
  glyc <- subset(master_df3_filtered, glyc == temp_res & loc == temp_loc)
  dis <- nrow(subset(glyc, APRdef2_tango== 0)) / nrow(subset(asp, APRdef2_tango == 0)) * 100
  apr <- nrow(subset(glyc, APRdef2_tango == 1 )) / nrow(subset(asp, APRdef2_tango == 1)) * 100
  gk_l <- nrow(subset(glyc, APRdef2_tango == 2 & Side == "N_ter")) / nrow(subset(asp, APRdef2_tango == 2 & Side == "N_ter")) * 100
  gk_r <- nrow(subset(glyc, APRdef2_tango == 2 & Side == "C_ter")) / nrow(subset(asp, APRdef2_tango == 2  & Side == "C_ter")) * 100
  fl1_l <- nrow(subset(glyc, APRdef2_tango == 3  & Side == "N_ter" )) / nrow(subset(asp, APRdef2_tango == 3  & Side == "N_ter")) * 100
  fl1_r <- nrow(subset(glyc, APRdef2_tango == 3 & Side == "C_ter" )) / nrow(subset(asp, APRdef2_tango == 3  & Side == "C_ter")) * 100
  fl2_l <- nrow(subset(glyc, APRdef2_tango  == 4  & Side == "N_ter" )) / nrow(subset(asp, APRdef2_tango  == 4  & Side == "N_ter")) * 100
  fl2_r <- nrow(subset(glyc, APRdef2_tango  == 4 & Side == "C_ter" )) / nrow(subset(asp, APRdef2_tango  == 4  & Side == "C_ter")) * 100
  all <- nrow(subset(glyc)) / nrow(subset(asp)) * 100
  dat2 <- c(dis,fl2_l,fl1_l,gk_l,apr,gk_r,fl1_r,fl2_r,all)
  bio_mouse[i,] <- dat2[1:8] / dat2[9]
  print(dat2[1:8] / dat2[9])
  print(nrow(glyc))
}
save(bio_mouse, file = "Data/RData/Mouse/bio_mouse.RData")
#Statistics for accessibility 
type <- "Sequon.Extra"
temp_loc <- strsplit(type, "\\.")[[1]][2]
temp_res <- strsplit(type, "\\.")[[1]][1]
glyc <- subset(master_df3_filtered, loc == temp_loc & Residue == "N")
glyc$PTM <- "No"
glyc$PTM[which(glyc$glyc == temp_res)] <- "Yes"
glyc$APRdef_tango <- paste0(glyc$APRdef_tango,"_",glyc$Side)
glyc_df <- as.matrix(table(glyc$APRdef_tango,glyc$PTM))
tot_prot <- c(sum(glyc_df[,1]),sum(glyc_df[,2]))
glyc_df <- rbind(glyc_df, tot_prot)
#Chi-square test of association  #Website: biostathandbook.com/chiind.html
PT = pairwiseNominalIndependence(glyc_df,
                                 compare = "row",
                                 fisher  = TRUE,
                                 gtest   = FALSE,
                                 chisq   = FALSE,
                                 method  = "fdr", 
                                 digits  = 3)
PT <- subset(PT, grepl("tot_prot", PT$Comparison, fixed = TRUE))
PT <- PT[order(PT$p.Fisher),]
rownames(PT) <- NULL 
PT$p.adj.Fisher <- PT$p.Fisher * (nrow(PT) / as.numeric(rownames(PT)))
PT$final <- NA
PT$final[which(PT$p.adj.Fisher < 0.05)] <- "*"
PT$final[which(PT$p.adj.Fisher < 0.01)] <- "**"
PT$final[which(PT$p.adj.Fisher < 0.001)] <- "***"
PT
```

STRESSES MS

```{r, include=FALSE}
master_df3_filtered$Side2 <- paste0(master_df3_filtered$APRdef2_tango,"_",master_df3_filtered$Side)
proteins_seq_ep <- unique(subset(master_df3_filtered, Side2 %in% c("1_None","2_N_ter","3_N_ter") & glyc %in% c("N-linked Glycosylation_N","Sequon") & loc == "Extra", select = 1))
proteins_seq_nep <- unique(subset(master_df3_filtered, glyc %in% c("N-linked Glycosylation_N","Sequon") & loc == "Extra" & !Protein %in% as.character(proteins_seq_ep$Protein),  select = 1))
proteins_other <- unique(subset(master_df3_filtered, loc == "Extra" & !Protein %in% c(as.character(proteins_seq_ep$Protein), as.character(proteins_seq_nep$Protein)),  select = 1))
proteins_intra <- unique(subset(master_df3_filtered, loc == "Intra" & !Protein %in% c(as.character(proteins_seq_ep$Protein),as.character(proteins_seq_nep$Protein), as.character(proteins_other$Protein)),  select = 1))
stresses_insoluble <- read.delim("Data/Mouse/Mouse_stresses/stresses_insoluble.tab")
stresses_insoluble1 <- subset(stresses_insoluble, Protein %in% proteins_seq_ep$Protein)
stresses_insoluble2 <- subset(stresses_insoluble, Protein %in% proteins_seq_nep$Protein)
stresses_insoluble3 <- subset(stresses_insoluble, Protein %in% proteins_other$Protein)
stresses_insoluble4 <- subset(stresses_insoluble, Protein %in% proteins_intra$Protein)
stresses_soluble <- read.delim("Data/Mouse/Mouse_stresses/stresses_soluble.tab")
stresses_soluble1 <- subset(stresses_soluble, Protein %in% proteins_seq_ep$Protein)
stresses_soluble2 <- subset(stresses_soluble, Protein %in% proteins_seq_nep$Protein)
stresses_soluble3 <- subset(stresses_soluble, Protein %in% proteins_other$Protein)
stresses_soluble4 <- subset(stresses_soluble, Protein %in% proteins_intra$Protein)
er_prots <- read.delim("Data/Mouse/Mouse_stresses/ER_stress.tab")
er_all1 <- subset(er_prots, Entry %in% proteins_seq_ep$Protein)
er_all2 <- subset(er_prots, Entry %in% proteins_seq_nep$Protein)
er_all3 <- subset(er_prots, Entry %in% proteins_other$Protein)
er_all4 <- subset(er_prots, Entry %in% proteins_intra$Protein)
hsp70_prots <- read.delim("Data/Mouse/Mouse_stresses/hsp70.tab")
hsp70_1 <- subset(hsp70_prots, Entry %in% proteins_seq_ep$Protein)
hsp70_2 <- subset(hsp70_prots, Entry %in% proteins_seq_nep$Protein)
hsp70_3 <- subset(hsp70_prots, Entry %in% proteins_other$Protein)
hsp70_4 <- subset(hsp70_prots, Entry %in% proteins_intra$Protein)
hsp90_prots <- read.delim("Data/Mouse/Mouse_stresses/hsp90.tab")
hsp90_1 <- subset(hsp90_prots, Entry %in% proteins_seq_ep$Protein)
hsp90_2 <- subset(hsp90_prots, Entry %in% proteins_seq_nep$Protein)
hsp90_3 <- subset(hsp90_prots, Entry %in% proteins_other$Protein)
hsp90_4 <- subset(hsp90_prots, Entry %in% proteins_intra$Protein)
OS_prots <- read.delim("Data/Mouse/Mouse_stresses/oxidative_stress.tab")
OS_1 <- subset(OS_prots, Entry %in% proteins_seq_ep$Protein)
OS_2 <- subset(OS_prots, Entry %in% proteins_seq_nep$Protein)
OS_3 <- subset(OS_prots, Entry %in% proteins_other$Protein)
OS_4 <- subset(OS_prots, Entry %in% proteins_intra$Protein)
prota_prots <- read.delim("Data/Mouse/Mouse_stresses/proteosome_inhibition.tab")
prota_1 <- subset(prota_prots, Entry %in% proteins_seq_ep$Protein)
prota_2 <- subset(prota_prots, Entry %in% proteins_seq_nep$Protein)
prota_3 <- subset(prota_prots, Entry %in% proteins_other$Protein)
prota_4 <- subset(prota_prots, Entry %in% proteins_intra$Protein)
```

TME binders

```{r, include=FALSE}
T_ctrBinder <- read.csv("Data/Mouse/TEM_binders/T_ctrBinder.csv")
T_tuniBinder <- read.csv("Data/Mouse/TEM_binders/T_tuniBinder.csv")
T_tuniBinder2<- T_tuniBinder[which(! T_tuniBinder$proteinID %in% T_ctrBinder$proteinID),]
tu1 <- subset(T_tuniBinder, proteinID %in% proteins_seq_ep$Protein)
tu2 <- subset(T_tuniBinder, proteinID %in% proteins_seq_nep$Protein)
tu3 <- subset(T_tuniBinder, proteinID %in% proteins_other$Protein)
tu4 <- subset(T_tuniBinder, proteinID %in% proteins_intra$Protein)
con1 <- subset(T_ctrBinder, proteinID %in% proteins_seq_ep$Protein)
con2 <- subset(T_ctrBinder, proteinID %in% proteins_seq_nep$Protein)
con3 <- subset(T_ctrBinder, proteinID %in% proteins_other$Protein)
con4 <- subset(T_ctrBinder, proteinID %in% proteins_intra$Protein)

tu11 <- subset(T_tuniBinder2, proteinID %in% proteins_seq_ep$Protein)
tu22 <- subset(T_tuniBinder2, proteinID %in% proteins_seq_nep$Protein)
tu33 <- subset(T_tuniBinder2, proteinID %in% proteins_other$Protein)
tu44 <- subset(T_tuniBinder2, proteinID %in% proteins_intra$Protein)
```

